\documentclass{ximera}
      
\title{Practice Exam 3}
      
\begin{document}
      
\begin{abstract}
      
This is the second practice exam.
      
\end{abstract}
      
\maketitle
       
 
 
 
 \textbf{USE FRACTIONS OR ROUND TO 4 DECIMAL PLACES}
 
\begin{enumerate}
\item A doctor tests 5 patients to measure their blood pressure, and each patient is 15\% likely to have high blood pressure.
\begin{enumerate}
\item Write out the Probability Distribution table for $X$:
\begin{itemize}
\item $P(0)=\answer{0.4437}$
\item $P(1)=\answer{0.3915}$
\item $P(2)=\answer{0.1382}$
\item $P(3)=\answer{0.0244}$
\item $P(4)=\answer{0.0022}$
\item $P(5)=\answer{0.0001}$
\end{itemize}



\item Find $E(X), Var,$ and $\sigma$.
\begin{itemize}
\item $E(X)=\answer{0.75}$
\item $Var=\answer{0.6375}$
\item $\sigma=\answer{0.7984}$
\end{itemize}



\item What is the probability that at most 3 patients have high blood pressure? $=\answer{0.9978}$
\item What us the probability at least 1 patients have high blood pressure? \\ \\Either $\answer{0.5563}$ (smaller) or $\answer{0.5564}$ (bigger)  depending on method and rounding. 
\item If I change the number of patients or the probability of high blood pressure, could we still do this problem?
\end{enumerate}
\item Consider the following ``probability distribution" tables, for each one determine if it in fact represents a probability distribution.  If no explain why, if yes compute $E(X), Var, \sigma$.   Use NA if there is no answer.
\begin{enumerate}
\item $$
\begin{array}{c|cccc}
X & 1 & 2 & 3 & 4\\
\hline
P(X) & 0.15 & 0.17 & 0.45 & 0.23
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{0.75}$
\item $Var=\answer{0.9424}$
\item $\sigma=\answer{0.9708}$
\end{itemize}




\item $$
\begin{array}{c|cccc}
X & 1 & 2 & 3 & 4\\
\hline
P(X) & 0.25 & 0.07 & 0.55 & 0.11
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{NA}$
\item $Var=\answer{NA}$
\item $\sigma=\answer{NA}$
\end{itemize}



\item $$
\begin{array}{c|cccc}
X & 0 & 1 & 2 & 3\\
\hline
P(X) & 0.25 & -0.07 & 0.52 & 0.2
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{NA}$
\item $Var=\answer{NA}$
\item $\sigma=\answer{NA}$
\end{itemize}


\item $$
\begin{array}{c|cccc}
X & 0 & 1 & 100 & 1000\\
\hline
P(X) & 0.25 & 0.25 & 0.25 & 0.25
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{275.25}$
\item $Var=\answer{176737.6875}$
\item $\sigma=\answer{420.4018}$
\end{itemize}



\item $$
\begin{array}{c|ccccc}
X & -2 & -1 & 0 & 1 & 2\\
\hline
P(X) & 0.22 & 0.27 & 0.31 & 0.11 & 0.09
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{-.42}$
\item $Var=\answer{1.4336}$
\item $\sigma=\answer{1.2015}$
\end{itemize}



\item $$
\begin{array}{c|cccc}
X & 1 & 2 & 3 & 4\\
\hline
P(X) & 0 & 0 & 1 & 0
\end{array}
$$

\begin{itemize}
\item $E(X)=\answer{3}$
\item $Var=\answer{0}$
\item $\sigma=\answer{0}$
\end{itemize}



\item $$
\begin{array}{c|cc}
X & A & B  \\
\hline
P(X) & p & 1-p
\end{array}
$$ assuming $0\leq p\leq 1$.

\begin{itemize}
\item $E(X)=\answer{Ap+(1-p)B}$
\item $Var=\answer{A^2p+(1-p)B^2-(Ap+(1-p)B)^2}$
\item $\sigma=\answer{(A^2p+(1-p)B^2-(Ap+(1-p)B)^2)^{(1/2)}}$
\end{itemize}




\end{enumerate}
\item A slot machine costs \$2 to play.  Each time you play, you have a 1/100 chance of winning 10 dollars, 1/1000 chance of winning 100 dollars and 1/1000000 chance of winning a million dollars.  You only win one of these prizes at a time.  When you play this game, what are your expected winnings/losses? The expected net winnings is $\answer{-.8}$ dollars.





\item Suppose the average weight of a rat is 22 oz, and rat weights are normally distributed with standard deviation 2 oz.
\begin{enumerate}
\item What is the probability that a random rat weighs between 20 and 23 oz.  $\answer{0.5328}$
\item What is the probability that a rat weights more than 21 oz? $\answer{0.6915}$
\item What is the probability a rat weighs less than 18 oz? $\answer{.0028}$
\item Ratty McRodent is said to weigh in the top 2\% of all rats.  What is the least that Ratty McRodent could weigh? $\answer{26.1075}$ oz.
\item Find the 1st and 3rd quartiles of this probability distribution.  The first quartile is $\answer{20.651}$ and the third is $\answer{23.349}$.
\item What is the probability that given 100 rats, their total weight is more than 2300 oz? It's $\answer{2.871}\times 10^{-7}$
\end{enumerate}
\item Suppose out of all cities in the United States, the numbers of annual robberies per hundred thousand citizens is normally distributed with mean 150  and standard deviation 40.
\begin{enumerate}
\item Given a random city, what is the probability that they have between 100 and 200 annual robberies per hundred thousand citizens? $\answer{0.7887}$.
\item Given a random city, what is the probability that they have more than annual 300 robberies per hundred thousand citizens? $\answer{8.8445}\times 10^{-5}$.
\item Find a number $k$ so that 30\% of cities have $k$ or more annual robberies per hundred thousand citizens. $k=\answer{170.976}$
\item What is the probability that 4 random cities have an average robbery rate less than 120 annual robberies per hundred thousand citizens? $\answer{0.668}$
\end{enumerate}
\item Suppose a storm is expected to strike the city of Madeupsville.  The storm is expected to arrive on November 25th but meteorologists can't nail down the exact time.  Instead the likely dates the storm will arrive are normally distributed, centered on November 25th, with standard deviation 5 days.
\begin{enumerate}
\item What is the probability that the storm arrives between the 19th and 26th of November? $\answer{0.4642}$

\item What is the probability that the storm arrives in December? $\answer{0.1151}$
\item Find $k$ so that the storm is 70\% likely to arrive within $k$ days of the 25th, before or after. $k=\answer{5.1822}$
\end{enumerate}
\item Consider the following probability distribution: $$
\begin{array}{c|cccc}
X & 0 & 1 & 100 & 1000\\
\hline
P(X)= & 0.35 & 0.15 & 0.45 & 0.05
\end{array}
$$

If I took 100 data points from this distribution and averaged them, what is the probability that this value is:
\begin{enumerate}
\item Over 100? $\answer{.41}$
\item Between 60 and 90? $\answer{0.355}$
\end{enumerate}


\end{enumerate}

 
 
      






\end{document}
