\documentclass{ximera}
      
\title{Practice Exam 2}
      
\begin{document}
      
\begin{abstract}
      
This is the second practice exam.
      
\end{abstract}
      
\maketitle
      
 \textbf{USE FRACTIONS OR ROUND TO 4 DECIMAL PLACES}
 
 \begin{enumerate}
\item What is the probability that I flip a coin 3 times and they all come up heads? $\answer{1/8}$
\item If I roll 2 dice, what is the probability that:
\begin{enumerate}
\item The sum of the outcomes is 7. $\answer{6/36}$
\item The sum of the outcomes is a 2. $\answer{1/36}$
\item The product of the outcomes is a 6. $\answer{4/36}$
\item The product of the outcomes is even. $\answer{3/4}$
\item The sum of the outcomes is a 13. $\answer{0}$
\end{enumerate}
\item Suppose I have 2 jars.  Jar one has 3 red marbles and 5 blue marbles.  Jar two has 2 red marbles and 4 green marbles.  If I pick a jar at random, and select a marble what is the chance that my marble is:
\begin{enumerate}
\item blue? $\answer{5/16}$
\item green? $\answer{1/3}$
\item red? $\answer{17/48}$
\end{enumerate}
\item Some people ordered some food at a restaurant, and over the course of  dinner, it becomes clear that some of the patrons are getting sick.  Consider this table representing how many people ordered what, and how many got sick:

$$\begin{tabular}{|c|c|c|c|}
\hline
 & Chicken & Fish & Steak \\
\hline
Got Sick & 5 & 4 & 3\\
\hline
Did Not Get Sick & 20 & 6 & 12\\
\hline
\end{tabular}$$
\begin{enumerate}
\item What is the probability that a random diner got sick? $\answer{12/50}$
\item What is the probability that a diner got sick if we knew they ate fish? $\answer{4/10}$
\item What is the probability that a random diner had fish or steak? $\answer{25/50}$
\item What is the probability that a random diner either had fish or got sick? $\answer{18/50}$
\item What is the probability that a diner ate steak, given that they got sick? $\answer{3/12}$
\item What food made you most likely to get sick? 

\begin{multipleChoice}
\choice{Chicken}
\choice[correct]{Fish}
\choice{Steak}
\end{multipleChoice}


\item Are the events ``Ate steak" and ``Got Sick" independent events?
\end{enumerate}
\item On a given day, there is a 10\% chance that it will rain, a 12\% chance that I will be in a bad mood and an 8\% chance that it will rain and I will be in a bad mood.
\begin{enumerate}
\item What is the probability that on a given day that it is raining and I am in a good mood? $\answer{.02}$
\item What is the probability that It is raining given that I am in a bad mood? $\answer{8/12}$
\item Are the events ``It is raining" and ``I am in a bad mood" independent events? 
\begin{multipleChoice}
\choice{Yes}
\choice[correct]{No}
\end{multipleChoice}

\end{enumerate}
\item Suppose that 500 people apply for a job, 240 of them are women, 300 had graduate degrees and 200 were women with graduate degrees.
\begin{enumerate}
\item How many men with graduate degrees applied for the job? $\answer{100}$
\item Are the events ``Applicant was a woman" and ``Applicant had a graduate degree" independent events?
\begin{multipleChoice}
\choice{Yes}
\choice[correct]{No}
\end{multipleChoice}

\end{enumerate}



\item At a graduate school, 60\% of their students are in STEM fields and 40\% are in the humanities.  Out of the STEM students, 30\% finish their degree, whereas in the humanities 45\% finish their degrees.
\begin{enumerate}
\item What is the probability that a random student  was a STEM concentration who did not finish? $\answer{.18}$
\item What is the probability that a given student finished their degree? $\answer{.36}$
\item What is the probability a student finished their degree or was a humanities concentration? $\answer{0.58}$
\item What is the probability that a given student who finished had a STEM concentration? $\answer{0.5}$
\item Are the events ``Student had a STEM concentration" and ``Student finished degree" independent events?
\begin{multipleChoice}
\choice{Yes}
\choice[correct]{No}
\end{multipleChoice}

\end{enumerate}
\item Suppose that a drug test has a 85\% chance of detecting drug use, but also has a 10\% chance of falsely indicating someone has used drugs.  Suppose that out of a group of people had this test administered to them, and 55\% of them tested positive.
\begin{enumerate}
\item What percent of these people actually used drugs? $\answer{0.6}$
\item What percent of these people used drugs and were tested positive? $\answer{.51}$
\item If someone was tested positive, what was the probability they were not on drugs? $\answer{.0727}$
\item What percent of these people were on drugs or tested positive for drugs? $\answer{.89}$
\end{enumerate}


\item If a salesman has to travel to 6 different cities, how many ways can he choose the order of cities to travel to? $\answer{720}$


\item Suppose a class has 5 seniors, 6 juniors, 6 sophomores and 4 freshman.
\begin{enumerate}
\item How many ways can I select 5 students to present homework solutions in front of the class? \answer{20349}
\item How many ways could I select 5 students if they were all juniors? $\answer{6}$
\item How many ways could I select 5 students if they were all non-freshman? $\answer{3003}$
\item How many ways could I select 5 students if they were all freshman? $\answer{0}$
\item How many ways could I select 5 students if they were all juniors or seniors? $\answer{462}$
\item What is the probability I select 5 students and they were all juniors? $\answer{6/20439}$
\item What is the probability I select 5 students and they were all non-freshman? $\answer{3003/20439}$
\item What is the probability I select 5 students and they were all freshman? $\answer{0}$
\item What is the probability I select 5 students and they were all juniors or seniors? $\answer{462/20439}$

\end{enumerate}

\item Suppose that you were poisoned, and out of 20 donuts, 5 have the antidote, and you need all 5 doses to live. 

\begin{enumerate}
\item How many ways can you pick 5 donuts to treat with the antidote? $\answer{15504}$
\item If you eat 5 donuts, what is the probability you live? $\answer{1/15504}$
\item If you eat 15 donuts, what is the probability you live? $\answer{3003/15504}$
\end{enumerate}
 


\end{enumerate}

 
 
      






\end{document}
